Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-10 edubots_surveys.Rnw
:refactor: to fill paragraphs
Eliminates commented out code and rewrites last paragraph

The success of this adoption largely depends on the willingness and ability of
teachers to embrace it, as they are the primary agents in this new educational
approach. As such, gathering and assessing feedback from these users will be
crucial in realizing the potential benefits of the technology.

@@

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed; this
  will be detailed in Section \ref{sec:meth}. The responses' analysis led to
the preparation of a second survey for teachers and 200 responses were
collected, again following the methodology that will be
  explained later. The questions of the second survey focused on asking about
  teachers' needs, opinions and preferences of the development of future
  technology-enhanced tools and its potential impact on educational institutions
  policies. In order to assess these, this paper layed out the following
  research questions:

@@

Contrarily to the mentioned chatbots that are focused on administrative tasks, teaching-oriented chatbots are more sophisticated, as they
set personalized learning outcomes and monitor learning progress. For instance,
\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
assistant chatbot developed on the Telegram messaging platform. In this study,
the Telegram platform was chosen because it is easy to use, students are familiar
with its features, and it enables them to exchange messages in different formats
(text, audio and video) \cite{fernoagua2018intelligent}. In addition, Telegram
can operate on all devices and operating systems. The ``eduAssistant'' chatbot
acts as an automatic agent in the teacher-content-student relationship, providing real-time
feedback loops and a personalized learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose questions to
their students and the chatbot assists those who need further help by giving
them more hints and reporting it to the educator's dashboard
\cite{fernoagua2018intelligent}. This could help educators identify
students who need more attention and provide them with more educational resources
relevant to their academic achievement. %In addition, a recent study
%has analysed how the use of chatbots positively affected the learning outcomes
%of students in a Chinese class \cite{doi:10.1177/0735633120929622}.

@@

We will present next the methodology we followed to find out teachers' opinions.

>>>>

Anyway, this adoption strongly depends on the compromise and capabilities of the teachers, as main active actors in this new academic approach. Given this,
asking and analyzing user's opinions with regard to this scenario will help reaping the expected benefits of the technology.

@@

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{black}{; this will be detailed in Section \ref{sec:meth}}. The responses' analysis
led to the preparation of a second survey for teachers and 200 responses were
collected\textcolor{black}{, again following the methodology that will be explained later. The questions of the second survey focused on asking about teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions policies. In order to assess these, this paper layed out the following research questions}:

@@

Contrarily to the mentioned chatbots that are focused on administrative tasks,
teaching-oriented chatbots are more sophisticated, as they set personalized
learning outcomes and monitor learning progress. For instance,
\cite{fernoagua2018intelligent} reported on ``eduAssistant'', a virtual teaching
assistant chatbot developed on the Telegram messaging platform. In this study,
the Telegram platform was chosen because it is easy to use, students are
familiar with its features, and it enables them to exchange messages in
different formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram can operate on all devices and operating systems. The
``eduAssistant'' chatbot acts as an automatic agent in the
teacher-content-student relationship, providing real-time feedback loops and a
personalized learning experience relevant to the students' acquired skills and
knowledge. Using this chatbot, educators can create interactive instances in
their lectures where they pose questions to their students and the chatbot
assists those who need further help by giving them more hints and reporting it
to the educator's dashboard \cite{fernoagua2018intelligent}. This could help
educators identify students who need more attention and provide them with more
educational resources relevant to their academic
achievement.

@@

Next, we will describe the methodology we employed to gather teachers' perspectives.
